\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
finish connection time section

\subsubsection{Connection time} 
{\color {blue} 
Connection time is the time from Tor Browser starup to the first successful Tor bootstrap. Non-finishing participants are assigned the maximum experiment time of 40:08. Table~\ref{table:participant-summary} summarizes the median connection times while Figure~\ref{fig:time_to_success_clamped} shows their distribution. Figure ~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.

%time observations (how long people took)
The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). 
The longer the time went on, the less likely that the participants were going to figure it out.

%time to success and version
Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$). That is, the differences in mean connection times in E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes). 
}

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08.
}
\label{fig:time_to_success_clamped}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
participants in E2 had finished, along with a minority of E3 participants. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

>>>>

\subsubsection{Connection time} 
Connection time is the time from Tor Browser starup to the first successful Tor bootstrap. Non-finishing participants are assigned the maximum experiment time of 40:08. Table~\ref{table:participant-summary} summarizes the median connection times while Figure~\ref{fig:time_to_success_clamped} shows their distribution. Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.

%time observations (how long people took)
The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$). Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.

%time to success and version
Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$). That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
The dots show the raw connection times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' (did not finish) numbers at the right show how many of participants 
did not finish, who were assigned the maximum time of 40:08.
}
\label{fig:time_to_success_clamped}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, shown continuously and at discrete times we found interesting.
For the purposes of plotting the cumulative distribution, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes. 
Notice that the longer the time went on, participants were less likely to succeed. 
At 1.5 minutes, every E1-NEW participant finished,
but only 58\% of E1-OLD had finished by that time.  
At 10 minutes, most participants in E2 had finished. 
}
\label{fig:time_to_success_ecdf}
\end{figure}
